QALY Comparison - Living Wage Intervention

### 2023-11-08 minos/testing/QALY_comparison_livingWage.Rmd
Added targets for calculating qalys on glasgow synthetic simulation runs

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'default_config')

>>>>

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')
